---
title: "Introduction to blblm"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{intro-to-blblm}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(blblm)
library(furrr)
```

### Test parallel

The package has been imporved by the power of parallelization. Firstly，you need to set the workers based on your computer.

Here, I can set the worker to 4. `set_worker(n = 4L)`. Notice that the number of 
workers should be **integer**, like 2L,3L ...

Then let's compare the speed :

```{r,eval=FALSE}
library(tictoc)

#  set_workers(n = 1L)
  tic()
  fit = fit <- blblm(mpg ~ wt * hp, data = mtcars, m = 4, B = 1000)
  t1 = toc()

  t1_elapsed = t1$toc - t1$tic
  t1_elapsed

  # parallel
  set_workers(n = 4L)
  tic()
  fit = fit <- blblm(mpg ~ wt * hp, data = mtcars, m = 4, B = 1000)
  t2 = toc()

  t2_elapsed = t2$toc - t2$tic
  
  t2_elapsed

```

### Test read files

```{r, eval=FALSE}
test_that("Test specify a list of file of datasets that would be then loaded in the workers", {

  dir.create(file.path(tempdir(),"test_data"),mode = "0777")
  tmp_data_path = normalizePath(file.path(tempdir(),"test_data"))

  data_list = split_data(mtcars,4)
  purrr::iwalk(1:4,
               ~vroom::vroom_write(data_list[[.x]],
                                   path = file.path(tmp_data_path,paste0(.x,".tsv")))
  )

  file_paths = list.files(tmp_data_path,full.names = TRUE)

  set_workers(n = 4L)

  blblm_files(mpg ~ wt * hp, file_paths = file_paths, B = 100)

  expect_invisible(blblm_files(mpg ~ wt * hp, file_paths = file_paths, B = 100))


})
```


### Estimate of bootstrap

```{r}
  fit <- blblm(mpg ~ wt * hp, data = mtcars, m = 3, B = 100)

  coef(fit)
  confint(fit, c("wt", "hp"))
  sigma(fit)
  sigma(fit, confidence = TRUE)
  predict(fit, data.frame(wt = c(2.5, 3), hp = c(150, 170)))
  predict(fit, data.frame(wt = c(2.5, 3), hp = c(150, 170)), confidence = TRUE)
```


### Logistic Regression

**blblm** package can also run a glm model, such as logistic regression.

```{r}
d.AD <- data.frame(treatment = gl(3,3),
                     outcome   = gl(3,1,9),
                     counts    = c(18,17,15, 20,10,20, 25,13,12))
glm_fit <- blbglm(counts ~ outcome + treatment, data = d.AD, family = poisson(),m = 1,B = 10)
coef(glm_fit)
```

